Predicting Infection Outbreak Dynamics in Toronto Healthcare Institutions: A Bayesian Approach

### 2024-12-15 paper/paper.qmd
Update paper.qmd
used references.bib

This dataset, entitled “Outbreaks in Toronto Healthcare Institutions” was obtained from Open Data Toronto on November 25, 2024 (Open Data Toronto, 2024) and possesses data from January 2nd, 2024 until November 20, 2024.. It is published by Toronto Public Health and documents infection outbreaks reported by various healthcare institutions in the city (the dataset is updated weekly on Thursday to capture the latest information). This is done in compliance with Ontario’s Health Protection and Promotion Act, which requires healthcare facilities to continuously report all infection outbreaks to their local authorities. This level of data collection allows timely identification and potential containment and reform in affected communities. 
For the purpose of this study, an infection outbreak (here on referred to as “outbreak”) is defined as a localized increase in the rate of infection above the baseline. In terms of settings, this dataset gathers information from hospitals (acute, psychiatric or chronic care), long term care homes (here on referred to as “LTCH”), retirement homes, and transitional care systems. Further, the dataset includes information about the type of outbreak (for eg., respiratory or enteric), location, the start and end date of the outbreak, and the causative agent(s). While Open Data Toronto possesses multiple other datasets regarding infections and outbreaks in Toronto, they were localised to information about homeless shelters or solely tracked COVID-19 outbreaks in the city. The chosen dataset encompasses a wider range of outbreak settings and includes various causative agents, including COVID-19, positioning it as a wider dataset - allowing us to extract greater insights and holistically understand the nature of infection outbreaks in Toronto.
For data cleaning, analysis and visualisation, this study uses R (R Core Team 2023), along with packages such as tidyverse for visualisation (Wickham et al. 2019), dplyr for data wrangling, and lubridate for handling temporal data. Further, ggplot2 was used for creating visualizations (Wickham, Chang, et al. 2023) and forcats for working with categorical variables. For the Bayesian analysis, rstanarm was and brms were used. Readr was used to read the structured data and scales allowed further development upon the visualisations. We also used ggeffects for visualisations of the model predictions and testthat for unit testing.

>>>>

This dataset, entitled “Outbreaks in Toronto Healthcare Institutions” was obtained from Open Data Toronto on November 25, 2024 (@opendatatoronto) and possesses data from January 2nd, 2024 until November 20, 2024. It is published by Toronto Public Health and documents infection outbreaks reported by various healthcare institutions in the city (the dataset is updated weekly on Thursday to capture the latest information). This is done in compliance with Ontario’s Health Protection and Promotion Act, which requires healthcare facilities to continuously report all infection outbreaks to their local authorities. This level of data collection allows timely identification and potential containment and reform in affected communities. 
For the purpose of this study, an infection outbreak (here on referred to as “outbreak”) is defined as a localized increase in the rate of infection above the baseline. In terms of settings, this dataset gathers information from hospitals (acute, psychiatric or chronic care), long term care homes (here on referred to as “LTCH”), retirement homes, and transitional care systems. Further, the dataset includes information about the type of outbreak (for eg., respiratory or enteric), location, the start and end date of the outbreak, and the causative agent(s). While Open Data Toronto possesses multiple other datasets regarding infections and outbreaks in Toronto, they were localised to information about homeless shelters or solely tracked COVID-19 outbreaks in the city. The chosen dataset encompasses a wider range of outbreak settings and includes various causative agents, including COVID-19, positioning it as a wider dataset - allowing us to extract greater insights and holistically understand the nature of infection outbreaks in Toronto.
For data cleaning, analysis and visualisation, this study uses R (@citeR), along with packages such as tidyverse for visualisation (@thereferencecanbewhatever), dplyr for data wrangling (@R-dplyr), and lubridate (@lubridate) for handling temporal data. Further, ggplot2 (@citeGgplot) was used for creating visualizations and forcats for working with categorical variables. For the Bayesian analysis, rstanarm (@rstanarm) and brms were used. Readr was used to read the structured data and scales allowed further development upon the visualisations (@citereadr). We also used ggeffects (@ggeffects) for visualisations of the model predictions and testthat for unit testing.
